---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# anyapi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/anyapi)](https://CRAN.R-project.org/package=anyapi)
[![Codecov test coverage](https://codecov.io/gh/jonthegeek/anyapi/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jonthegeek/anyapi?branch=main)
[![R-CMD-check](https://github.com/jonthegeek/anyapi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jonthegeek/anyapi/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Tools to interactively query hundreds of web 'APIs', with documentation.

## Installation

You can install the development version of anyapi from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jonthegeek/anyapi")
```

## Usage

Find an API.
Such APIs can be used with {beekeeper} to create an API wrapper package.

```{r basic-usage}
library(anyapi)
find_api("trello")
```

## Code of Conduct

Please note that the anyapi project is released with a [Contributor Code of Conduct](https://jonthegeek.github.io/anyapi/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
